### 2012-10-30 paper_sean/results.tex
before adding the 3 headed figure monster

\begin{table}
\begin{center}
\begin{tabular}{|l|r|r|r|r|}
\hline
                                         &              & Simulated  & Real Vel. & Real Vel.  \\
                                         & Evaluations  & Velocity &    (CCML)     & (ROBIN) \\
\hline
Parameterized gaits + optimization \cite{yos:clune}   &153    & --    & 5.8 & --\\
\hline
HyperNEAT in hardware \cite{yos:clune}                 & 180         & --         &   9.7  & --   \\
\hline
RL PoWER Spline \cite{haocheng}                         & 300         & --         &   11.1 & --\\
\hline
GA + simulator \cite{glette}             & 60000       & *16.7       &   13.0   & \textbf{17.8}  \\
\hline
HyperNEAT + simulator [this paper]                     & 40000       & \textbf{25.4}       &   \textbf{14.5} & --\\
\hline
\end{tabular}
\end{center}
\tablabel{results}
\caption{Velocities of learned gaits in simulation and on two different copies of the QuadraTot robot. Subject to availability, data are reported from the experiments for this paper and three previous studies. Reported are the total number of evaluations per run, the average of the fastest gaits produced in each run in simulation, and the fastest gait produced on a physical robot, either the QuadraTot in the Cornell Creative Machines Lab (CCML) or the QuadraTot in the Robotics and Intelligent Systems (ROBIN) lab at the University of Oslo. *Instead of using the single fitness value reported in~\cite{glette}, we ran 19 additional runs and used the average fitness of those 20 runs. Velocities are in cm/s, and bold indicates the best performance.}  
\end{table}

>>>>

\begin{table}
\begin{center}
\begin{tabular}{|l|r|r|r|r|}
\hline
                                         &              & Simulated  & Real Vel. & Real Vel.  \\
                                         & Evaluations  & Velocity &    (CCML)     & (ROBIN) \\
\hline
Parameterized gaits + optimization \cite{yos:clune}   &153    & --    & 5.8 & --\\
\hline
HyperNEAT in hardware \cite{yos:clune}                 & 180         & --         &   9.7  & --   \\
\hline
RL PoWER Spline \cite{haocheng}                         & 300         & --         &   11.1 & --\\
\hline
GA + simulator \cite{glette}             & 60000       & *16.7       &   13.0   & \textbf{17.8}  \\
\hline
HyperNEAT + simulator [this paper]                     & 40000       & \textbf{25.4}       &   \textbf{14.5} & --\\
\hline
\end{tabular}
\end{center}
\tablabel{results}
\caption{Velocities of learned gaits in simulation and on two different copies of the QuadraTot robot. Subject to availability, data are reported from the experiments for this paper and three previous studies. Reported are the total number of evaluations per run, the average of the fastest gaits produced in each run in simulation, and the fastest gait produced on two different copies of the QuadraTot robot (CCML and ROBIN, see text). *Instead of using the single fitness value reported in~\cite{glette}, we ran 19 additional runs and used the average fitness of those 20 runs. Velocities are in cm/s, and bold indicates the best performance.}  
\end{table}
